Page not found

### 2023-06-20 manuscript/chapters/2_neural_fields.qmd
finish figures for chap. 2

::: {.content-visible when-format="html"}
![Simulation of the Gaussian network of neurons with $p=1$. Every neuron is represented by a dot, of which the height represents its activity level, and the colorbar doubles as a y-axis.](figures/embedding_d=1.mp4){#fig-p1}
:::

@@

::: {.content-visible when-format="html"}
![(TODO remove overlap, change notation, scatter only) Simulation of the Gaussian network of neurons with $p=2$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/embedding_d=2_h0=0.mp4){width=500px #fig-p2}
:::

::: {.content-visible when-format="pdf"}
![(TODO PDF remove overlap, change notation, scatter only) Simulation of the Gaussian network of neurons with $p=2$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/lol7.jpg){width=500px #fig-p2}
:::

@@

![(TODO animation in 3D, rename non-cycling to original, number from one) Intuition for the cycling behavior by considering the recurrent currents](figures/cycling_recurrent.png){#fig-cycling-irec}

@@

::: {.content-visible when-format="html"}
![A cycling neural field with $\delta=6$ and initial condition $h(z_1, z_2, t < 0) = z_1$. The latent trajectory is also computed, and demonstrates the oscillatory behaviour.](figures/embedding_d=2_h0=0_cycling_delta=6.mp4){#fig-cycling-anim}
:::

@@

![(TODO) CDF of the Gaussian distribution](figures/1920px-Normal_Distribution_CDF.svg.png){width=400px #fig-gaussian-cdf}

@@

Defining the neural field in $[0,1]^p$ also addresses the problem that we tried to hide in @sec-gridmethod relating to the difficulties of defining a grid on $\Rp$. With the integral on $[0,1]^p$, we can simply use a uniform grid, which maps back to samples in $\Rp$ by using the inverse CDF, as shown in @fig-sampling-R2-012.

![(TODO not color) A grid in $[0,1]^2$ and the corresponding samples in $\R^2$. The numeric density of points in $\R^2$ approaches the normal distribution as the grid becomes finer.](figures/sampling_R2_01.png){#fig-sampling-R2-012}

>>>>

::: {.content-visible when-format="html"}
![Simulation of the Gaussian network of neurons with $p=1$. Every neuron is represented by a dot, of which the height represents its activity level, and the colorbar doubles as a y-axis.](figures/embedding_p=1.mp4){#fig-p1}
:::

@@

::: {.content-visible when-format="html"}
![Simulation of the Gaussian network of neurons with $p=2$. Every neuron is represented by a dot, of which the height represents its activity level. Projections are shown by gray points.](figures/embedding_p=2.mp4){width=500px #fig-p2}
:::

::: {.content-visible when-format="pdf"}
![(TODO PDF) Simulation of the Gaussian network of neurons with $p=2$. Every neuron is represented by a dot, of which the height represents its activity level. Projections are shown by gray points.](figures/lol7.jpg){width=500px #fig-p2}
:::

@@

```{python}
#| label: fig-cycling-irec
#| fig-cap: Intuition for the cycling behavior. We consider the network in the state $h(z_1,z_2)=z_1$, and look at the recurrent currents. The recurrent currents align with the activity for the original neural field, and the effective change in potential is zero everywhere. For the cycling neural field, the recurrent currents are orthogonal to the activity, such that with the decay term, the effective change leads to a rotation in the counter-clockwise direction, towards the state $h(z_1,z_2)=z_2$.
#| echo: false

from matplotlib.image import NonUniformImage

nrec = 6
rnn_nocyc = LowRankRNN.new_sampled_valentin(
	phi=sigmoid, mapping_samples=ReshapeMapping.new_nrec(nrec=nrec).inverse_samples(),
	I_ext=zero, exclude_self_connections=False
)
rnn_cyc = LowRankCyclingRNN.new_sampled_valentin(
	phi=sigmoid, mapping_samples=ReshapeMapping.new_nrec(nrec=nrec).inverse_samples(),
	I_ext=zero, exclude_self_connections=False, delta=10, shift=1
)
rnn_cyc.h_lagging = lambda t, h: h  # HACK : make the recurrent currents work for t=0

fig, axes = plt.subplots(ncols=3, nrows=2, figsize=(3*4-3, 2*3), layout='constrained')

for i, rnn in enumerate([rnn_nocyc, rnn_cyc]):
	axes[i, 0].set_aspect('equal')
	axes[i, 0].set_xlabel('$z_1$')
	axes[i, 0].set_ylabel('$z_2$')
	shape = (2**nrec, 2**nrec)
	im = axes[i, 0].pcolormesh(
		rnn.F[:, 0].reshape(shape), rnn.F[:, 1].reshape(shape), rnn.phi(rnn.F[:, 0]).reshape(shape),
		cmap=cmap_bi, vmin=0, vmax=1,
		rasterized=True  # enable rasterization to prevent 50Mo SVG files, lol
	)
	breathe(axes[i, 0])
	if i == 1:
		plt.colorbar(im, ax=axes[i, 0], orientation='horizontal', label='$\\phi(h(z_1,z_2))$')

	axes[i, 1].set_aspect('equal')
	axes[i, 1].set_xlabel('$z_1$')
	axes[i, 1].set_ylabel('$z_2$')
	im = axes[i, 1].pcolormesh(
		rnn.F[:, 0].reshape(shape), rnn.F[:, 1].reshape(shape), rnn.I_rec(0, rnn.F[:, 0]).reshape(shape),
		cmap='coolwarm', vmin=-2, vmax=2,
		rasterized=True  # enable rasterization to prevent 50Mo SVG files, lol
	)
	breathe(axes[i, 1])
	if i == 1:
		plt.colorbar(im, ax=axes[i, 1], orientation='horizontal', label='$I^\mathrm{rec}(z_1, z_2)$')

	axes[i, 2].set_aspect('equal')
	axes[i, 2].set_xlabel('$z_1$')
	axes[i, 2].set_ylabel('$z_2$')
	im = axes[i, 2].pcolormesh(
		rnn.F[:, 0].reshape(shape), rnn.F[:, 1].reshape(shape), rnn.dh(0, rnn.F[:, 0]).reshape(shape),
		cmap=cmap_pan, vmin=-2, vmax=2, shading='gouraud',
		rasterized=True  # enable rasterization to prevent 50Mo SVG files, lol
	)
	breathe(axes[i, 2])
	if i == 1:
		plt.colorbar(im, ax=axes[i, 2], orientation='horizontal', label='$\partial_t h(z_1, z_2)$')

add_headers(axes=axes.flat, row_headers=['Original neural field', 'Cycling neural field'], fontsize='medium', row_pad=8)
add_headers(axes=axes.flat, col_headers=['Neural activity', 'Recurrent currents', 'Effective change'], fontsize='medium', col_pad=8)

for ax in axes.flat:
	mktrans(fig, ax)

# %matplotlib inline
display(fig)
```

@@

::: {.content-visible when-format="html"}
![A cycling neural field with $\delta=6$ and initial condition $h(z_1, z_2, t < 0) = z_1$. The latent trajectory is also computed, and demonstrates the oscillatory behaviour.](figures/embedding_p=2_cycling.mp4){#fig-cycling-anim}
:::

@@

```{python}
#| label: fig-gaussian-cdf
#| fig-cap: CDF of the Gaussian distribution
#| echo: false
#| 
from scipy import stats

z = np.linspace(-4.5, 4.5, 200)
fig, ax = plt.subplots()
ax.plot(z, stats.norm.cdf(z), clip_on=False)
# ax.set_xlim((-4, 4))
ax.set_ylim((0, 1))
ax.set(xlabel='$z$', ylabel='$\\mathrm{CDF}(z)$')
ax.set_yticks([0.0, 0.25, 0.5, 0.75, 1.0])
ax.grid(clip_on=False)
# ax.grid(clip_on=False, axis='y')
# breathe(ax, which='x')
# breathe(ax, which='y', pad_frac=0.1)
breathe(ax)
mktrans(fig, ax)
display(fig)
```

@@

Defining the neural field in $[0,1]^p$ also addresses the problem that we tried to hide in @sec-gridmethod relating to the difficulties of defining a grid on $\Rp$. With the integral on $[0,1]^p$, we can simply use a uniform grid, which maps back to samples in $\Rp$ by using the inverse CDF, as shown in @fig-grid-correspondance.

```{python}
#| label: fig-grid-correspondance
#| fig-cap: A grid in $[0,1]^2$ and the corresponding samples in $\R^2$. The numeric density of points in $\R^2$ approaches the normal distribution as the grid becomes finer (here, the mesh size is $2^{-4}$ along each dimension).
#| echo: false

nrec = 4
mapping = ColumnMapping.new_nrec(nrec=nrec)
Y = mapping.inverse_samples()
Z = stats.norm.ppf(Y)

fig, axes = plt.subplots(ncols=2, figsize=(8, 3))
axes[0].scatter(*Y.T, c='k', s=15)
axes[1].scatter(*Z.T, c='k', s=15)
axes[0].set_xlim((0,1))
axes[0].set_ylim((0,1))
axes[0].set_aspect('equal')
axes[1].set_aspect('equal')
axes[0].set_title('In $[0,1]^2$ (CDF space)', fontsize='medium')
axes[1].set_title('In $\\mathbb{R}^2$ (PDF space)', fontsize='medium')
breathe(axes[0])
breathe(axes[1])
mktrans(fig, axes[0])
mktrans(fig, axes[1])
display(fig)
```
